---
title: "Company Bankruptcy"
author: "Group 5"
date: "11/22/2021"
output: 
html_document:
    toc: true
    theme: readable
    highlight: tango
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Load and treat data
```{r}

#testing Raph vhghjhvj
#testing Gabe 123
CompanyData <- read.csv("company.csv", stringsAsFactors = TRUE)
str(CompanyData)
summary(CompanyData)

#TO-DO 1
#library(caret)
#set.seed(12345)
#CompanyData_trainup <- upSample(x=CompanyData[,-which(colnames(CompanyData)=="Bankrupt.")], y=CompanyData$Bankrupt.)

# Normalize
normalize <- function(x) {
  return ((x - min(x)) / (max(x) - min(x)))
}

CompanyData_norm <- as.data.frame(lapply(CompanyData, normalize))

CompanyData_norm$Bankrupt.<- as.factor(CompanyData_norm$Bankrupt.)

CompanyData_norm$Net.Income.Flag <- NULL

summary(CompanyData_norm)
str(CompanyData_norm)


```

## Upsample

```{r}
library(caret)
CompanyData_ups <- as.data.frame(upSample(CompanyData[,-1],as.factor(CompanyData_norm$Bankrupt.)))

str(CompanyData_ups)
summary(CompanyData_ups)

```
## Train and test
```{r}
# Randomized cut
set.seed(12345)
CompanyData_ups <- CompanyData_ups[sample(nrow(CompanyData_ups)),]

set.seed(12345)
test_set <- sample(1:nrow(CompanyData_ups), nrow(CompanyData_ups)*.25) 

CompanyData_ups_test <- CompanyData_norm[test_set,]
CompanyData_ups_train <- CompanyData_norm[-test_set,]

#summary(CompanyData_ups_train)
#nrow(CompanyData_ups_train)
#nrow(CompanyData_ups_test)
summary(CompanyData_ups)
```
#TO-DO 2
#Create each model with some form of improvement

## Neural Networks
```{r}
library(neuralnet)
```
### Run model

```{r, cache = TRUE}
m_ann <- neuralnet(formula = as.numeric(as.character(Class)) ~ ., data = CompanyData_ups, hidden = 3,stepmax = 1e8)
str(CompanyData_ups)
```
```{r}
plot(m_ann)
```
### Evaluate results
```{r}

m_ann_results <- compute(m_ann, CompanyData_ups)
m_ann_prediction <- m_ann_results$net.result
head(m_ann_prediction)
summary(m_ann_prediction)
head(CompanyData_ups)

#m_ann_prediction_ID <- data.frame(m_ann_prediction, CompanyData_norm_test$ID)
#head(m_ann_prediction_ID)

m_ann_binary <- ifelse(m_ann_prediction >= 0.5, 1,0)
table(m_ann_binary)
table(CompanyData_ups$Class)

library(caret)
confusionMatrix(as.factor(m_ann_binary), as.factor(CompanyData_ups$Class), positive = "1")

summary(as.factor(m_ann_prediction))

```


## Logistic regression model
### Run model

```{r}

simplemodel <- glm(Class ~ ., data = CompanyData_ups, family = binomial(link = "logit"), maxit = 1e8)
#summary(simplemodel)

```

### Stepwise Regression to find significant variables

```{r}
stepmodel <- step(simplemodel, direction = "backward")
summary(stepmodel)
```

### Prediction based on Step Model

```{r}
pred_step <- predict(simplemodel, CompanyData_ups, type = "response")
summary(pred_step)
pred_cat <- ifelse(pred_step >= 0.5, 1, 0)

```

### Evaluting results

```{r}
library(caret)
confusionMatrix(as.factor(pred_cat), as.factor(CompanyData_ups$Class), positive = "1")
```
## SVM
### Run model
```{r}
library(kernlab)
```
```{r}
m_svm <- ksvm(as.factor(Class) ~ ., data = CompanyData_ups, kernel = "rbfdot")

m_svm

```
```{r}

m_svm_prediction <- predict(m_svm,CompanyData_ups)

head(m_svm_prediction)
summary(m_svm_prediction)

agreement_sum <- m_svm_prediction == CompanyData_ups$Class

prop.table(table(agreement_sum))

confusionMatrix(as.factor(m_svm_prediction), as.factor(CompanyData_ups$Class), positive = "1")


```

### Decision Tree 
## Run Model
```{r}
library(C50)
CompanyData_ups$Class <- as.factor(CompanyData_ups$Class)
decision_tree_model <- C5.0(Class ~ ., data = CompanyData_ups)
plot(decision_tree_model)
```

## Evaluate Results
```{r}
decision_tree_model_result <- predict(decision_tree_model, CompanyData_ups)
str(decision_tree_model_result)
summary(decision_tree_model_result)

library(gmodels)
library(caret)
confusionMatrix(as.factor(decision_tree_model_result), as.factor(CompanyData_ups$Class), positive = '1')
```

## KNN 
## Run Model
```{r}
#KNN needs its x and y values separate
library(class)
knn_x <- CompanyData_ups[ ,-which(colnames(CompanyData_ups) == "Class")]
knn_label <- CompanyData_ups[ , which(colnames(CompanyData_ups) == "Class")]


knn_model <- knn(train = knn_x, knn_x, cl = knn_label, k = 5)

library(caret)

confusionMatrix(as.factor(knn_model), as.factor(CompanyData_ups$Class), positive = '1')
```

#TO-DO 3
##Create the level 2 model (decision tree)